Fiber Collision Correction Method for BOSS Power Spectrum

### 2015-03-25 fc_paper/fc_paper.tex
Abstract updated, intro updated
Finished edits up to Section 2.

\begin{abstract}
Redshift surveys, including BOSS, use fiber fed spectrographs. A fiber is used for each galaxy in order obtain its redshift. However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information. In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated. Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
\end{abstract}
\keywords{cosmology: observations --- }

\section{Introduction} 
\begin{itemize}
\item fiber-fed multi-object spectroscopic surveys allow us to collect large redshift data, which is why it?s the favorite of cosmology surveys
\item moving from statistics dominated regime to systematics dominated regime
\end{itemize}

Redshift surveys, including BOSS, use fiber fed spectrographs. A fiber is used for each galaxy in order obtain its redshift. However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information. In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated. Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.

Fiber-collision corrections such as that proposed by \cite{Guo:2012aa} have been applied to correct for the two point correlation function. Guo et al. (2012) estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey. Unfortunately, this method cannot be easily extended for the fourier counter parts to the two-point and three-point correlation functions due to the complex geometry of the overlapping regions. Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the powerspectrum/bispectrum estimator.

In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
% Include cosmology assumption and out line of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (CITE CITE). By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.

A direct way of understanding the effects of fiber-collisions on clustering statistics in observations is to first apply fiber-collisions to mock catalogues then compare the clustering statistics obtained from mock catalogues with and without the fiber collisions. Afterwards, correction methods for fiber-collisions can be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they can reproduce the clustering statistics of the original mock catalogues without fiber-collisions. The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber-collisions and improves the clustering measurements.

@@

Effects of fiber-collisions must be understood and interpreted in conjunction with these systematic effects and to ultimately test our fiber-collision correction method we use LasDamas (\citealt{McBride:2009aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues. These mocks have already been used in interpreting observational results for BOSS and are generated through different prescriptions. Therefore they provide complementary tests fiber-collisions and our correction method tailored for BOSS. 
% Include brief detail on what each mock has to offer

Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies". More specifically, the LasDamas Galaxy mock catalogues is constructed from the N-body Large Suite of Dark Matter Simulations (LasDamas). The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation. The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa}). The HOD prescription is specified so that the galaxy mock catalogues reproduce the correlation function of the SDSS sample. % Detail about the geometry and redshift range 
\begin{itemize}
\item above description is not entirely correct because that was LasDamas for Guo+2011
\item SDSS-II Geometry
\item lower redshift range
\end{itemize}

Next, the QPM mock galaxy catalogues uses a "quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume. The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations. Afterward the \cite{Tinker:2012aa} HOD parameterization is used to populate the halos. The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsamped based on angular sky completeness (sector completeness) and radial selection. The QPM mock galaxy catalogue is generated using the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.25$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. For a detailed description of the QPM galaxy mock catalogues we refer readers to \cite{White:2014aa}.

Finally the Tiling Mock catalogue is generated using 
\begin{itemize}
\item documentation for tiling mock? 
\end{itemize}

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies. The redshift distributions illustrate the constant $\bar{n}(z)$ for the LasDamas mock catalogue, while the QPM and Tiling mock $\bar{n}(z)$ distributions trace the observed BOSS redshift distribution.

% insert transition that mentions how the main clustering statistics we focus on in this paper is the Power Spectrum
In order to measure the power spectrum for these mock catalogues, we use the standard \cite{Feldman:1994aa} (FKP) estimator. Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}.
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. More specifically, $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues Las Damas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator. The width of the $P(k)$ for Las Damas and QPM represent the sample variance ($\Delta P(k)/\overline{P(k)}$) calculated from the multiple mock catalogues. We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement. We remind readers that the $\overline{P(k)}$ of the LasDamas mock catalogues is an outlier because of the different redshift range compared to the other mock catalogues.} \label{fig:mockpk}
\end{center}
\end{figure}

For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum, Figure \ref{fig:mockpk}. For the $P(k)$ in Figure \ref{fig:mockpk}, we do not apply the fiber-collisions to the catalogues. Therefore, there are no complications from using the exact formulation of Equation \ref{eq:fkppk}. However, when we calculate $P(k)$ for BOSS DR12 data in Figure \ref{fig:mockpk} (\cmasscolor), the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation}
must be taken account (\citealt{Anderson:2012aa, Beutler:2014aa}). Hence, instead of the galaxy density $n_g({\bf r})$ we use a weighted galaxy density $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$ and instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$. For LasDamas and QPM, which have multiple mock catalogues, we compute the sample variance of the power spectrum
\begin{equation} \label{eq:pk_var}
\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{mock}} \sum\limits_i^{N_\mathrm{mock}} (P_i(k)- \overline{P(k)})^2 }. 
\end{equation}
$\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.

>>>>

\begin{abstract}
Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies. However, the physical size of the fibers limit these surveys from successfully collecting redshifts from galaxies within the angular fiber-collision scale, which ultimately lead to significant systematic effects on galaxy clustering measurements. Using simulated mock catalogues, which have been extensively used in interpreting large-scale structure clustering results (such as the correlation function and power spectrum) of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the galaxy power spectrum in particular. We compare the methods currently used to correct for fiber-collisions in the literature and assess their success in reconstructing the true power spectrum for mock catalogues.

We present our fiber-collision correction method, which statistically reconstructs the clustering of fiber-collided pairs, using the distribution of the line-of-sight displacements between resolved fiber-collided pairs, and properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we successfully reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$. Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that the method can be validated and calibrated in actual observations. With statistical precision no longer obstructing galaxy clustering measurements, our correction method will allows us constrain systematic effects of fiber-collisions and extend power spectrum measurements to smaller scales. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

\section{Introduction} 
Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs.

For each galaxy, a fiber is used to obtain a spectroscopic redshift. However, due to the physical size of the fibers even with efficient targeting strategies (e.g. \citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to separately extract the spectroscopic information (\citealt{Yoon:2008aa} {\bf CITE MORE}). In these situations, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured. With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.

As our cosmological surveys extend further to higher redshifts, the systematic effect becomes worse as the fiber-collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales. SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$. This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey redshift redshift range, and fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}). Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and must be understood as these measurements probe to smaller scales and as higher order statistics such as the three-point correlation function or the bispectrum are used in cosmological studies. Perhaps with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) will render fiber-collisions obsolete. However, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.

To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}). For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor. This provides a reasonable correction for the fiber-collision effects at scales much larger than the fiber-collision scales; however the correction falls short near the fiber-collision scale. In fact, as \cite{Zehavi:2005aa} find, fiber-collisions affect the two-point correlation function (2PCF) measurements even on scales significantly larger than the fiber-collision scale ( $> 1\;\mathrm{Mpc}/h$). For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber-collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}). While this shot-noise term adjustment has been calibrated within the mock catalogues used to interpret the BOSS clustering results, validating these methods for observations remains a challenge.

Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber-collision correction method for the 2PCF that is able to reasonably correct for fiber-collisions above and below the collision scale. \cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber-collisions. Unfortunately, this method cannot be applied to the Fourier clustering measurements due to the complex geometry of the overlapping regions. As a result, we propose a fiber-collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber-collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and proper accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.

In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogues with realistic applied fiber-collisions and power spectrum estimator used throughout the paper. Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber-collisions of power spectrum measurements and test and compare common correction methods. Afterwards, we present our correction method in Section \ref{sec:apply}, test it on the mock catalogues, and compare it to other correction methods. Finally in Section \ref{sec:summary} we summarize and discuss our results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogues play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Guo:2012aa, Manera:2013aa} {\bf LIST MORE}) since systematic effects can be simulated on the mock catalogues. This allows us to test how these effects influence clustering measurements and devise correction methods that attempt to account for these effects.

A direct way of understanding the effects of fiber-collisions on clustering statistics in observations is to first apply fiber-collisions to mock catalogues then compare the clustering statistics obtained from mock catalogues with and without the fiber collisions. Correction methods for fiber-collisions can then be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogues without fiber-collisions. The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber-collisions and improves the clustering measurements.

@@

Effects of fiber-collisions must be understood and interpreted in conjunction with these systematic effects. Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions. Therefore they provide complementary tests fiber-collisions and our correction method tailored for BOSS.

Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies". % Include brief detail on what each mock has to offer

The LasDamas Galaxy mock catalogues is constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$. The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation. The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa, McBride:2011aa}). The HOD prescription is specified so that the galaxy mock catalogues reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$. The LasDamas galaxy mock catalogues have 40 realizations that spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7. They also include redshift space distortions from velocities, but do not model fiber-collisions.

To model the fiber-collisions of the observed galaxies in BOSS, we impose fiber-collisions at the angular scale of $62''$. Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it. Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogues are affected by fiber-collisions.

Next, the QPM mock galaxy catalogues uses a "quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume. The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations. Afterward the \cite{Tinker:2012aa} HOD parameterization is used to populate the halos. The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsamped based on angular sky completeness (sector completeness) and radial selection. Furthermore, QPM mocks model the fiber-collisions of the BOSS CMASS sample ($62''$ angular fiber-collision scale). The QPM galaxy mock catalogue uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$. We use 1000 realizations of the QPM galaxy mock catalogue. For a detailed description of the QPM galaxy mock catalogues we refer readers to \cite{White:2014aa}.

Finally the Tiling Mock catalogue is generated using

{\bf INSERT TILING MOCK DESCRIPTION HERE}

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies. The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution.

% insert transition that mentions how the main clustering statistics we focus on in this paper is the Power Spectrum
In order to measure the power spectrum for these mock catalogues in our investigation, we use the standard \cite{Feldman:1994aa} (FKP) estimator. Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}: 
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues Las Damas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator. The width of the $P(k)$ for Las Damas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogues. We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement. We remind readers that the LasDamas mock catalogue has an overall greater $\overline{P(k)}$ due to the fact that the catalogue spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogues.} \label{fig:mockpk}
\end{center}
\end{figure}

For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum in Figure \ref{fig:mockpk}. For the $P(k)$ in Figure \ref{fig:mockpk}, we do not apply the fiber-collisions to the catalogues. Therefore, there are no complications from using the exact formulation of Equation \ref{eq:fkppk}. When we calculate $P(k)$ for BOSS Data Release 12 data (\cmasscolor) in Figure \ref{fig:mockpk}, however, the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation}
must be taken account (\citealt{Anderson:2012aa, Beutler:2014aa}). Hence, instead of the galaxy density $n_g({\bf r})$ we use a weighted galaxy density $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$ and instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$. For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
\begin{equation} \label{eq:pk_var}
\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{realization}} \sum\limits_i^{N_\mathrm{realization}} (P_i(k)- \overline{P(k)})^2 }. 
\end{equation}
$N_\mathrm{realization}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P_i(k)$ is the power spectrum for each realization. $\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.
